---
title: "NEWS"
author: Erik.Leppo@tetratech.com and jon.harcum@tetratech.com
output: github_document
---
<!-- NEWS.md is generated from NEWS.Rmd. Please edit that file -->

```{r Options, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "NEWS-"
)
```

```{r LastUpdate, echo = FALSE}
cat(paste0("Last Update: ",Sys.time()))
```

baytrends_files v0.7.19
===========
Released - 2024-10-11

* fix: Update new 2023 to filter out data without plots

baytrends_files v0.7.18
===========
Released - 2024-10-10

* refactor: Move 2022 data files to 'old' folder
* refactor: Update current with new data
* refactor: Add 2023 data, plots
* refactor: Update pick_files for new data

baytrends_files v0.7.17
===========
Released - 2023-10-12

* refactor: Update text on "no plot" graph

baytrends_files v0.7.16
===========
Released - 2023-09-28

* fix: Update 'current' data files with '2022' data files.

baytrends_files v0.7.15
===========
Released - 2023-09-28

* fix: Updated 2022 data
    + Files 2 and 4 blank and all data in files 1 and 2
    + data\2022
* fix: Updated ProcessData_ShinyData_2022.R to include more QC checks

baytrends_files v0.7.14
===========
Released - 2023-09-27

* docs: Rename ReadMe file in data directory

baytrends_files v0.7.13
===========
Released - 2023-09-27

* refactor: Add 2022 plots

* refactor: Update current plots to 2022

baytrends_files v0.7.12
===========
Released - 2023-09-27

* refactor: Add 2022 data

* refactor: Update current data to 2022

baytrends_files v0.7.11
===========
Released - 2023-08-16

* docs: Add more comments for non-R users to yearly process data script

     + Added to 2021 file in data-raw folder

baytrends_files v0.7.10
===========
Released - 2023-08-16

* docs: Add documentation about provenance and naming of data sets

* docs: Add documentation about how to update repository for new data sets

baytrends_files v0.7.9
===========
Released - 2023-08-03

* refactor: Reorganize folders into a more workable structure, Issue #4

* docs: Update ReadMe with file structure information, Issue #4

* docs: Added a ReadMe file to the data folder

baytrends_files 0.7.8
===========
Released - 2022-12-16

* refactor:  Rename 2021 "test" folder to "2021", Issue #3

baytrends_files 0.7.7
===========
Released - 2022-11-29

* fix: Update 2021 data files in test folder, Issue #3

baytrends_files 0.7.6
===========
Released - 2022-11-21

* refactor: Create data-raw folder and add old data and processing scripts
    + 2019 and 2020
* refactor: Add 2021 data and processing script, Issue #3

baytrends_files 0.7.5
===========
Released - 2022-11-18

*fix: Rename files to old naming convention

baytrends_files 0.7.4
===========
Released - 2022-11-18

* refactor: Add data to test folder

baytrends_files 0.7.3
===========
Released - 2022-11-18

* refactor: Add test folder for 2021 data plots for testing

baytrends_files 0.7.2
===========
Released - 2022-07-20

* refactor: Update GitHub repo so it doesn't include "old" files after adding
back to local file location

baytrends_files 0.7.1
===========
Released - 2022-07-20

* refactor: Update GitHub repo so it doesn't include "old" files
* refactor: Remove "old" files

baytrends_files 0.7
===========
Released - 2022-07-18

* fix: Update "no data" plot text to exclude DIN and PO4 parameters

baytrends_files 0.6
===========
Released - 2022-07-18

* fix: Update combination of files from six to four, Issue #1

baytrends_files 0.5
===========
Released - 2022-07-18

* fix: Update data files for consistenty, Long Term, Issue #2
    + File names, pick list, folder, no data plot, period in csv
* refacator: Move old data files to "old" subdirectory of data

baytrends_files 0.4
===========
Released - 2022-07-15

* refactor: Combine data files from 6 to 4, Issue #1

baytrends_files 0.3
===========
Released - 2022-07-14

* refactor: Combine data files from 6 to 4, Issue #1

baytrends_files 0.2
===========
Released - 2022-03-15

* refactor: Revised figures with new format (Rebecca Murphy)


baytrends_files 0.1.0.9014
===========
Released - 2022-01-18

* feature: Added background PDF, TidalWaterQualityChange.pdf

baytrends_files 0.1.0.9013
===========
Released - 2021-12-08

* refactor: Update 2020 data gamName with basic wording to match 2019 data

baytrends_files 0.1.0.9012
===========
Released - 2021-12-08

* refactor: Update 2020 data files to ensure have most current version

baytrends_files 0.1.0.9011
===========
Released - 2021-12-07

* fix: Update 2020 data files with mapLayer (version 2)

baytrends_files 0.1.0.9010
===========
Released - 2021-12-06

* fix: Update 2020 data files with mapLayer

baytrends_files 0.1.0.9009
===========
Released - 2021-12-06

* refactor: Update data files for 2020
    + Rename FullPeriod files with year
    + Keep picklist.csv for each year
    + Did not update plots

baytrends_files 0.1.0.9008
===========
Released - 2021-09-15

* refactor: Update pick_files.csv with boolean value for showing plots

baytrends_files 0.1.0.9007
===========
Released - 2021-09-15

* feature: Add additional directories for other data sets
* refactor: Update pick_files.csv with plot directory names

baytrends_files 0.1.0.9006
===========
Released - 2021-09-15

* refactor: Renamed plots folder, baytrends map issue 50
    + https://github.com/tetratech/baytrendsmap/issues/50
* refactor: Add Flow Adjusted plots folder
* docs: Updated README
* docs: Add DESCRIPTION

baytrends_files 0.1.0.9005
===========
Released - 2021-09-08

* Added "_no_plot.png" to plot folder for use when Shiny app uses data other
than 'Full Period'.

baytrends_files 0.1.0.9005
===========
Released - 2021-09-08

* Added "_no_plot.png" to plot folder for use when Shiny app uses data other
than 'Full Period'.

baytrends_files 0.1.0.9004
===========
Released - 2021-08-16

* docs: Update README with proper URL for accessing data files

baytrends_files 0.1.0.9003
===========
Released - 2021-08-16

* Add data folder
    + Moved files out of Shiny app to this repo
    + Includes list of files and pick list names for the Shiny app

baytrends_files 0.1.0.9002
===========
Released - 2021-05-19

* sample png files added to directory nlt_fp
* created Rproj
* added nlt_fp directory

baytrends_files 0.1.0.9001
===========
Released - 2021-05-19

* refactor: Initial commit
* docs: Add README
* docs: Add LICENSE
* docs: Add .Rbuildignore
* docs: Add NEWS