---
title: "NEWS"
author: Erik.Leppo@tetratech.com and jon.harcum@tetratech.com
output: github_document
---
<!-- NEWS.md is generated from NEWS.Rmd. Please edit that file -->

```{r Options, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "NEWS-"
)
```

```{r LastUpdate, echo = FALSE}
cat(paste0("Last Update: ",Sys.time()))
```

baytrends_files 0.1.0.9011
===========
Released - 2021-12-07

* fix: Update 2020 data files with mapLayer (version 2)

baytrends_files 0.1.0.9010
===========
Released - 2021-12-06

* fix: Update 2020 data files with mapLayer

baytrends_files 0.1.0.9009
===========
Released - 2021-12-06

* refactor: Update data files for 2020
    + Rename FullPeriod files with year
    + Keep picklist.csv for each year
    + Did not update plots

baytrends_files 0.1.0.9008
===========
Released - 2021-09-15

* refactor: Update pick_files.csv with boolean value for showing plots

baytrends_files 0.1.0.9007
===========
Released - 2021-09-15

* feature: Add additional directories for other data sets
* refactor: Update pick_files.csv with plot directory names

baytrends_files 0.1.0.9006
===========
Released - 2021-09-15

* refactor: Renamed plots folder, baytrends map issue 50
    + https://github.com/tetratech/baytrendsmap/issues/50
* refactor: Add Flow Adjusted plots folder
* docs: Updated README
* docs: Add DESCRIPTION

baytrends_files 0.1.0.9005
===========
Released - 2021-09-08

* Added "_no_plot.png" to plot folder for use when Shiny app uses data other
than 'Full Period'.

baytrends_files 0.1.0.9005
===========
Released - 2021-09-08

* Added "_no_plot.png" to plot folder for use when Shiny app uses data other
than 'Full Period'.

baytrends_files 0.1.0.9004
===========
Released - 2021-08-16

* docs: Update README with proper URL for accessing data files

baytrends_files 0.1.0.9003
===========
Released - 2021-08-16

* Add data folder
    + Moved files out of Shiny app to this repo
    + Includes list of files and pick list names for the Shiny app

baytrends_files 0.1.0.9002
===========
Released - 2021-05-19

* sample png files added to directory nlt_fp
* created Rproj
* added nlt_fp directory

baytrends_files 0.1.0.9001
===========
Released - 2021-05-19

* refactor: Initial commit
* docs: Add README
* docs: Add LICENSE
* docs: Add .Rbuildignore
* docs: Add NEWS