---
title: "README"
author: Erik.Leppo@tetratech.com and jon.harcum@tetratech.com
output: github_document
---
<!-- NEWS.md is generated from README.Rmd. Please edit that file -->

```{r Options, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "NEWS-"
)
```

```{r LastUpdate, echo = FALSE}
cat(paste0("Last Update: ",Sys.time()))
```

# baytrends_files

Repository to store baytrends R package outputs to be used with maps.

<!-- badges: start -->

<!-- badges: end -->

# Installation

No installation as these files are meant to be accessed by the baytrendsmap Shiny app.

Production version:

<https://baytrends.chesapeakebay.net/baytrendsmap/>

Testing version:

<https://tetratech-wtr-wne.shinyapps.io/baytrendsmap/>

# File Access

Example code to access files.

``` r
url_data <- "https://raw.githubusercontent.com/tetratech/baytrends_files/main/data/"
df_data <- read.csv(paste0(url_data, "pick_files.csv")) 
```

# Naming Scheme

Plot files are named in a consistent manner to make them easy to parse and identify (Station_Parameter_MapLayer).

Map Layer:

-   B = Bottom

-   S = Surface

Plots are in folders with the following naming scheme:

-   NLT = Non-Linear Trend

-   FA = Flow Adjusted

-   T or F = TRUE or FALSE (Flow Adjusted)

-   ST or FT = Short Term or Long Term

# File Structure

All files to be served up to the Shiny app are in the folder "data".

Each year will have its own folder and the current files will be in the folder "current_year".

The CBP version of the app hosts these files on their own servers for faster response times.

# Updates

More information on file structure and yearly updates in "data/ReadMe_data.txt"
